\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.35in}

\raggedright
\setlength{\tabcolsep}{0in}
\pdfgentounicode=1

% Section formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\large\bfseries
}{}{0em}{}[\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Sanket Trivedi} \\ \vspace{3pt}
    \small
    \faPhone* ~ (+91) 99256 02832 \quad
    \faEnvelope* ~ \href{mailto:trivedisanket2004@gmail.com}{trivedisanket2004@gmail.com} \quad
    \faLinkedin ~ \href{https://www.linkedin.com/in/sanket-trivedi-pandit/}{LinkedIn} \quad
    \faGithub ~ \href{https://github.com/snkttrivedi}{GitHub} \quad
    \faCode ~ \href{https://leetcode.com/u/SANKET_TRIVEDI/}{LeetCode}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Indian Institute of Information Technology, Vadodara}{Dec 2022 -- 2026}
  {B.Tech in Computer Science and Engineering}{}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading {devx AI labs}{January 2026 -- Present} {\textbf{Software Development Engineer Intern}}{}

 \resumeItemListStart
  \resumeItem{Architected a \textbf{scalable component library} by migrating hardcoded layouts to \textbf{reusable, token-driven components} using design system principles, reducing UI duplication by  \textbf{40\%} and accelerating feature development velocity.}

  \resumeItem{Designed \textbf{reusable content models} using \textbf{Strapi (Headless CMS)} and integrated them via APIs to enable \textbf{dynamic, CMS-driven UI rendering}.}

  \resumeItem{Improved frontend performance using \textbf{code-splitting} and ensuring smoother rendering for data-heavy pages.}
\resumeItemListEnd
  

\resumeSubheading
  {Pistalix Software Solutions}{May 2025 -- Jul 2025}
  {\textbf{Project Management \& Frontend Developer Intern}}{Surat, Gujarat}

\resumeItemListStart
  \resumeItem{Led \textbf{client requirement gathering} and translated \textbf{business requirements} into technical solutions for an AR-based jewelry visualization platform.}

  \resumeItem{Designed and developed an interactive \textbf{3D AR Ring Viewer} using \textbf{React} and \textbf{Three.js}, focusing on realistic rendering and seamless user experience.}

  \resumeItem{Collaborated with \textbf{clients and stakeholders} through iterative feedback cycles to refine features, align deliverables, and improve overall product usability.}

  \resumeItem{Built \textbf{reusable frontend components} and optimized application performance through \textbf{model compression}, rendering improvements, and lighting optimization.}
\resumeItemListEnd



%-----------PROJECTS-----------
\section{Projects}
\resumeProjectHeading
{\textbf{Three.js Hand Interactions} $|$ Three.js, MediaPipe Hands, Vanilla JS, HTML/CSS
\hspace{0.8em} \href{https://github.com/snkttrivedi/threejs-hand-interactions}{\faGithub}
\hspace{0.5em} \href{https://threejs-hand-interactions.vercel.app/}{\faExternalLink*}}
{}
\resumeItemListStart
  \resumeItem{Developed a real-time \textbf{AR experience} demonstrating gesture-based \textbf{3D object manipulation} using \textbf{MediaPipe} and \textbf{Three.js}.}
  \resumeItem{Engineered precision hand tracking to detect \textbf{21 3D landmarks} on each hand for wireframe shape interaction with zero build dependencies.}
  \resumeItem{Implemented physics-based controls for \textbf{pinch gestures} (resize, cycle shapes) and object touch detection to trigger dynamic neon color changes.}
\resumeItemListEnd
\vspace{0.3em}

{\textbf{Loan Recommendation Platform} $|$ Gemini API, React, TypeScript, REST APIs
\hspace{0.8em} \href{https://github.com/snkttrivedi/loan_app}{\faGithub}}
{}
\resumeItemListStart
  \resumeItem{Built a platform that helps users discover \textbf{suitable loan options} based on their financial inputs and preferences.}

  \resumeItem{Developed responsive UI workflows using \textbf{React} with reusable components for form handling and user interaction.}

  \resumeItem{Integrated \textbf{REST APIs} to handle user data flow and support loan recommendation logic.}

  \resumeItem{Implemented an \textbf{AI-powered chatbot} to provide \textbf{Q\&A support} and help users understand recommended loan options.}
\resumeItemListEnd

%-----------SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{

\textbf{Languages:} C/C++, JavaScript, TypeScript, SQL \\
\vspace{2pt}

\textbf{Frontend Technologies:} React.js, Three.js, WebXR, HTML5/CSS3, Tailwind CSS, Responsive Design \\
\vspace{2pt}

\textbf{Backend \& APIs:} Node.js, Express.js, REST APIs, Strapi (Headless CMS), API Integration \\
\vspace{2pt}

\textbf{Databases:} PostgreSQL, MongoDB, Redis, Supabase, MySQL \\
\vspace{2pt}

\textbf{Tools \& Platforms:} Git, GitHub, Docker, Vercel, VS Code, Postman \\
\vspace{2pt}

\textbf{Core Fundamentals:} Data Structures \& Algorithms, Object-Oriented Programming (OOP), DBMS, Operating Systems \\
\vspace{2pt}

\textbf{Soft Skills:} Teamwork, Communication, Leadership, Problem Solving, Stakeholder Collaboration

}}
\end{itemize}

%-----------ACHIEVEMENTS-----------

\section{Leadership \& Achievements}
\resumeItemListStart
  \resumeItem{\textbf{Logistics Lead, MLSA IIIT Vadodara} — Coordinated logistics and operations for campus technical events and workshops.}
  \resumeItem{\textbf{Convener / Co-Convener, Technical Fest} — Managed planning and execution of Valorant esports events and team coordination.}
\resumeItemListEnd

\end{document}